Funding programmes for early career researchers do/not influence their independence

### 2023-06-09 article.Rmd
visualisations added to article

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(targets)
library(dplyr)
library(cobalt)
library(knitr)
library(psych)
library(kableExtra)
```

@@

### Missing data
```{r echo=FALSE}
d <- tar_read(full_indicator)
na_counts <- sum(is.na(d$RII))
na_percentage <- round((na_counts / nrow(d))*100, 1)

@@

```{r echo=FALSE}
d <- tar_read(full_indicator)
na_counts <- sum(is.na(d$RII))

@@

# Print tables in R Markdown
knitr::kable(balance_stats_1, caption = "Balance Statistics: Treatment vs Control Group 1")
knitr::kable(balance_stats_2, caption = "Balance Statistics: Treatment vs Control Group 2")

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(targets)
library(dplyr)
library(cobalt)
library(knitr)
library(psych)
library(kableExtra)
library(ggplot2)
```

@@

### Missing data
```{r echo=FALSE}
d <- tar_read(full_indicator)
d$disc_ford <- as.factor(d$disc_ford)

na_counts <- sum(is.na(d$RII))
na_percentage <- round((na_counts / nrow(d))*100, 1)

@@

# assuming df is your dataframe
df <- r_after_final

@@

# Print tables in R Markdown
knitr::kable(balance_stats_1, caption = "Balance Statistics: Treatment vs Control Group 1") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
knitr::kable(balance_stats_2, caption = "Balance Statistics: Treatment vs Control Group 2") %>% kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))

@@

Was there a difference between the treatment groups in their level of independence before the intervention?

The analysis of variance (ANOVA) was used to compare the means of the three treatment groups. The results of the ANOVA showed that the effect of treatment was not statistically significant (F(2, 630) = 0.256, p = 0.613). The mean square (MS) within groups was 0.05775, which indicates that the variability within each group is relatively small. The MS between groups was 0.01476, which is smaller than the MS within groups, suggesting that the differences between the means of the treatment groups are small. The model explained only a small proportion of the total variance in the data (R-squared = 0.01). Sixty-five observations were deleted due to missing data. In conclusion, there is no evidence to suggest that the treatment has a significant effect on the outcome variable. However, the small effect size and the missing data should be taken into consideration when interpreting the results. Post-hoc test power was 0.9997622 as calculated by GPower (Faul, Erdfelder, Lang & Buchner, 2007).

```{r echo=FALSE}
set.seed(123)

d_before <- r_before_final

before_treatment <- aov(RII ~ treatment, data = d_before)
summary(before_treatment)

means_before_treatment <- aggregate(RII ~ treatment, data = d_before, FUN = mean)

ggplot(data = means_before_treatment, aes(x = treatment, y = RII)) +
         geom_bar(stat = "identity", position = "dodge") +
         labs(x = "Treatment", y = "Mean RII") +
         theme_bw()

Further, were there any differences in independence across disciplines?

```{r echo=FALSE}
set.seed(123)

d_before$disc_ford <- substring(d_before$disc_ford, 0, 1)
d_before$disc_ford <- as.factor(d_before$disc_ford)

d_before$treatment <- as.factor(d_before$treatment)

table(d_before$disc_ford, by = d_before$treatment)

disc_before <- aov(RII ~ disc_ford, data = d_before)
summary(disc_before)

means_before_disc <- aggregate(RII ~ disc_ford, data = d_before, FUN = mean)

ggplot(data = means_before_disc, aes(x = disc_ford, y = RII)) +
         geom_bar(stat = "identity", position = "dodge") +
         labs(x = "disc_ford", y = "Mean RII") +
         theme_bw()

Was there any interaction between the treatment group and discipline?

```{r echo=FALSE}
set.seed(123)

before_disc_interaction <- aov(RII ~ treatment*disc_ford, data = d_before)
summary(before_disc_interaction)

 means_before_disc_interaction <- aggregate(RII ~ treatment + disc_ford, data = d_before, FUN = mean)

     # Plot grouped bar plot
     ggplot(data = means_before_disc_interaction, aes(x = treatment, y = RII, fill = disc_ford)) +
         geom_bar(stat = "identity", position = "dodge") +
         labs(x = "Treatment", y = "Mean RII") +
         scale_fill_discrete(name = "disc_ford") +
         theme_bw()

Was there a difference between the treatment groups in their level of independence after the intervention?

The analysis of variance (ANOVA) was used to compare the means of the three treatment groups. The results of the ANOVA showed that the effect of treatment was not statistically significant (F(2, 630) = 0.256, p = 0.613). The mean square (MS) within groups was 0.05775, which indicates that the variability within each group is relatively small. The MS between groups was 0.01476, which is smaller than the MS within groups, suggesting that the differences between the means of the treatment groups are small. The model explained only a small proportion of the total variance in the data (R-squared = 0.01). Sixty-five observations were deleted due to missing data. In conclusion, there is no evidence to suggest that the treatment has a significant effect on the outcome variable. However, the small effect size and the missing data should be taken into consideration when interpreting the results. Post-hoc test power was 0.9997622 as calculated by GPower (Faul, Erdfelder, Lang & Buchner, 2007).

```{r echo=FALSE}
set.seed(123)

d_before <- r_after_final

before_treatment <- aov(RII ~ treatment, data = d_before)
summary(before_treatment)

means_before_treatment <- aggregate(RII ~ treatment, data = d_before, FUN = mean)

ggplot(data = means_before_treatment, aes(x = treatment, y = RII)) +
         geom_bar(stat = "identity", position = "dodge") +
         labs(x = "Treatment", y = "Mean RII") +
         theme_bw()

Further, were there any differences in independence across disciplines?

```{r echo=FALSE}
set.seed(123)

d_before$disc_ford <- substring(d_before$disc_ford, 0, 1)
d_before$disc_ford <- as.factor(d_before$disc_ford)

d_before$treatment <- as.factor(d_before$treatment)

table(d_before$disc_ford, by = d_before$treatment)

disc_before <- aov(RII ~ disc_ford, data = d_before)
summary(disc_before)

means_before_disc <- aggregate(RII ~ disc_ford, data = d_before, FUN = mean)

ggplot(data = means_before_disc, aes(x = disc_ford, y = RII)) +
         geom_bar(stat = "identity", position = "dodge") +
         labs(x = "disc_ford", y = "Mean RII") +
         theme_bw()

Was there any interaction between the treatment group and discipline?

```{r echo=FALSE}
set.seed(123)

before_disc_interaction <- aov(RII ~ treatment*disc_ford, data = d_before)
summary(before_disc_interaction)

 means_before_disc_interaction <- aggregate(RII ~ treatment + disc_ford, data = d_before, FUN = mean)

     # Plot grouped bar plot
     ggplot(data = means_before_disc_interaction, aes(x = treatment, y = RII, fill = disc_ford)) +
         geom_bar(stat = "identity", position = "dodge") +
         labs(x = "Treatment", y = "Mean RII") +
         scale_fill_discrete(name = "disc_ford") +
         theme_bw()

### Intervention effect

d <- all 
d$treatment <- as.factor(d$treatment)
d$independence_timing <- as.factor(d$independence_timing)

interaction <- aov(RII ~ treatment * independence_timing, data = d)
summary(interaction)
heplots::etasq(interaction, anova = TRUE)

 ###calculating r-squared - generated by chatGPT, so not sure this is correct

     n <- nrow(d)
     p <- length(coef(interaction))
     SSresid <- sum(resid(interaction)^2)
     SStotal <- sum((na.omit(d$RII) - mean(d$RII, na.rm = TRUE))^2)
     R2 <- 1 - (SSresid / SStotal)
     adjR2 <- 1 - ((1 - R2) * (n - 1) / (n - p - 1))

 ### visualisations

means <- aggregate(RII ~ treatment + independence_timing, data = d, FUN = mean)

 ggplot(data = interaction, aes(x = treatment, y = RII, fill = independence_timing)) +
         geom_violin(scale = "width") +
         scale_fill_discrete(name = "Independence Timing", labels = c("After intervention", "Before intervention")) +
         xlab("Treatment Group") +
         ylab("RII Score") +
         ggtitle("Violin Plot of RII Scores by Treatment and Time") +
         theme_bw()
